Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2020-06-03 doc/network.tex
using bbl instead

\bibliography{networkprsb}
\end{document}

>>>>

\begin{thebibliography}{10}

\bibitem{anderson1991infectious}
Anderson RM and May RM.
\newblock 1991 {\em Infectious diseases of humans: dynamics and control}.
\newblock Oxford university press.

\bibitem{diekmann1990definition}
Diekmann O, Heesterbeek JAP, and Metz JA.
\newblock 1990 On the definition and the computation of the basic reproduction
  ratio {R0} in models for infectious diseases in heterogeneous populations.
\newblock {\em J. Math. Biol}.
\newblock {\bfseries 28}, 365--382.

\bibitem{kribs2000simple}
Kribs-Zaleta CM and Velasco-Hern{\'a}ndez JX.
\newblock 2000 A simple vaccination model with multiple endemic states.
\newblock {\em Math. Biosci}.
\newblock {\bfseries 164}, 183--201.

\bibitem{van2002reproduction}
Van~den Driessche P and Watmough J.
\newblock 2002 Reproduction numbers and sub-threshold endemic equilibria for
  compartmental models of disease transmission.
\newblock {\em Math. Biosci}.
\newblock {\bfseries 180}, 29--48.

\bibitem{smith2012ross}
Smith DL, Battle KE, Hay SI, Barker CM, Scott TW, and McKenzie FE.
\newblock 2012 {Ross, Macdonald, and a theory for the dynamics and control of
  mosquito-transmitted pathogens}.
\newblock {\em PLoS Pathog}.
\newblock {\bfseries 8}.

\bibitem{dietz1993estimation}
Dietz K.
\newblock 1993 The estimation of the basic reproduction number for infectious
  diseases.
\newblock {\em Stat. Methods Med. Res}.
\newblock {\bfseries 2}, 23--41.

\bibitem{chowell2003sars}
Chowell G, Fenimore PW, Castillo-Garsow MA, and Castillo-Chavez C.
\newblock 2003 {SARS outbreaks in Ontario, Hong Kong and Singapore: the role of
  diagnosis and isolation as a control mechanism}.
\newblock {\em J. Theor. Biol}.
\newblock {\bfseries 224}, 1--8.

\bibitem{mills2004transmissibility}
Mills CE, Robins JM, and Lipsitch M.
\newblock 2004 Transmissibility of 1918 pandemic influenza.
\newblock {\em Nature}.
\newblock {\bfseries 432}, 904.

\bibitem{nishiura2009transmission}
Nishiura H, Castillo-Chavez C, Safan M, and Chowell G.
\newblock 2009 {Transmission potential of the new influenza A (H1N1) virus and
  its age-specificity in Japan}.
\newblock {\em Euro Surveill}.
\newblock {\bfseries 14}, 19227.

\bibitem{nishiura2010pros}
Nishiura H, Chowell G, Safan M, and Castillo-Chavez C.
\newblock 2010 {Pros and cons of estimating the reproduction number from early
  epidemic growth rate of influenza A (H1N1) 2009}.
\newblock {\em Theor. Biol. Med. Model}.
\newblock {\bfseries 7}, 1.

\bibitem{ma2014estimating}
Ma~J, Dushoff J, Bolker BM, and Earn DJ.
\newblock 2014 Estimating initial epidemic growth rates.
\newblock {\em Bull. Math. Biol}.
\newblock {\bfseries 76}, 245--260.

\bibitem{wearing2005appropriate}
Wearing HJ, Rohani P, and Keeling MJ.
\newblock 2005 Appropriate models for the management of infectious diseases.
\newblock {\em PLoS Med}.
\newblock {\bfseries 2}, e174.

\bibitem{svensson2007note}
Svensson {\AA}.
\newblock 2007 A note on generation times in epidemic models.
\newblock {\em Math. Biosci}.
\newblock {\bfseries 208}, 300--311.

\bibitem{roberts2007model}
Roberts M and Heesterbeek J.
\newblock 2007 Model-consistent estimation of the basic reproduction number
  from the incidence of an emerging infection.
\newblock {\em J. Math. Biol}.
\newblock {\bfseries 55}, 803.

\bibitem{wallinga2007generation}
Wallinga J and Lipsitch M.
\newblock 2007 How generation intervals shape the relationship between growth
  rates and reproductive numbers.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 274}, 599--604.

\bibitem{park2019practical}
Park SW, Champredon D, Weitz JS, and Dushoff J.
\newblock 2019 A practical generation-interval-based approach to inferring the
  strength of epidemics from their speed.
\newblock {\em Epidemics}.
\newblock {\bfseries 27}, 12--18.

\bibitem{champredon2015intrinsic}
Champredon D and Dushoff J.
\newblock 2015 Intrinsic and realized generation intervals in
  infectious-disease transmission.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 282}.

\bibitem{kenah2008generation}
Kenah E, Lipsitch M, and Robins JM.
\newblock 2008 Generation interval contraction and epidemic data analysis.
\newblock {\em Math. Biosci}.
\newblock {\bfseries 213}, 71--79.

\bibitem{nishiura2010time}
Nishiura H.
\newblock 2010 Time variations in the generation time of an infectious disease:
  implications for sampling to appropriately quantify transmission potential.
\newblock {\em Math. Biosci. Eng}.
\newblock {\bfseries 7}, 851--869.

\bibitem{tomba2010some}
Scalia~Tomba G, Svensson {\AA}, Asikainen T, and Giesecke J.
\newblock 2010 Some model based considerations on observing generation times
  for communicable diseases.
\newblock {\em Math. Biosci}.
\newblock {\bfseries 223}, 24--31.

\bibitem{britton2019estimation}
Britton T and Scalia~Tomba G.
\newblock 2019 Estimation in emerging epidemics: {Biases} and remedies.
\newblock {\em J. Royal Soc. Interface}.
\newblock {\bfseries 16}, 20180670.

\bibitem{trapman2016inferring}
Trapman P, Ball F, Dhersin JS, Tran VC, Wallinga J, and Britton T.
\newblock 2016 Inferring {R0} in emerging epidemics--the effect of common
  population structure is small.
\newblock {\em J. Royal Soc. Interface}.
\newblock {\bfseries 13}.

\bibitem{hampson2009transmission}
Hampson K, Dushoff J, Cleaveland S, Haydon DT, Kaare M, Packer C, and Dobson A.
\newblock 2009 Transmission dynamics and prospects for the elimination of
  canine rabies.
\newblock {\em PLoS Biol}.
\newblock {\bfseries 7}.

\bibitem{who2014ebola}
{WHO Ebola Response Team} .
\newblock 2014 {Ebola virus disease in West Africa--the first 9 months of the
  epidemic and forward projections}.
\newblock {\em N. Engl. J. Med}.
\newblock {\bfseries 371}, 1481--1495.

\bibitem{svensson2015influence}
Svensson {\AA}.
\newblock 2015 The influence of assumptions on generation time distributions in
  epidemic models.
\newblock {\em Math. Biosci}.
\newblock 270, 81--89.

\bibitem{heesterbeek1996concept}
Heesterbeek J and Dietz K.
\newblock 1996 The concept of {R0} in epidemic theory.
\newblock {\em Stat. Neerl}.
\newblock {\bfseries 50}, 89--110.

\bibitem{diekmann2000mathematical}
Diekmann O and Heesterbeek JAP.
\newblock 2000 {\em Mathematical epidemiology of infectious diseases: model
  building, analysis and interpretation}, volume~5.
\newblock John Wiley \& Sons.

\bibitem{roberts2004modelling}
Roberts M.
\newblock 2004 Modelling strategies for minimizing the impact of an imported
  exotic infection.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 271}, 2411--2415.

\bibitem{aldis2005integral}
Aldis G and Roberts M.
\newblock 2005 An integral equation model for the control of a smallpox
  outbreak.
\newblock {\em Math. Biosci}.
\newblock {\bfseries 195}, 1--22.

\bibitem{Champredon2018equivalence}
Champredon D, Dushoff J, and Earn DJD.
\newblock 2018 {Equivalence of the Erlang-distributed SEIR epidemic model and
  the renewal equation}.
\newblock {\em SIAM J. Appl. Math}.
\newblock 78, 3258--3278.

\bibitem{lotka1907relation}
Lotka AJ.
\newblock 1907 Relation between birth rates and death rates.
\newblock {\em Science}.
\newblock {\bfseries 26}, 21--22.

\bibitem{fraser2007estimating}
Fraser C.
\newblock 2007 Estimating individual and household reproduction numbers in an
  emerging epidemic.
\newblock {\em PloS One}.
\newblock {\bfseries 2}.

\bibitem{ball1997epidemics}
Ball F, Mollison D, and Scalia-Tomba G.
\newblock 1997 Epidemics with two levels of mixing.
\newblock {\em Ann. Appl. Probab}.
\newblock pages 46--89.

\bibitem{ball2002general}
Ball F and Neal P.
\newblock 2002 A general model for stochastic {SIR} epidemics with two levels
  of mixing.
\newblock {\em Math. Biosci}.
\newblock {\bfseries 180}, 73--102.

\bibitem{yan2008separate}
Yan P.
\newblock 2008 Separate roles of the latent and infectious periods in shaping
  the relation between the basic reproduction number and the intrinsic growth
  rate of infectious disease outbreaks.
\newblock {\em J. Theor. Biol}.
\newblock {\bfseries 251}, 238--252.

\bibitem{leskovec2016snap}
Leskovec J and Krevl A.
\newblock 2014 {SNAP} {Datasets}: {Stanford Large Network Dataset Collection}.
\newblock http://snap.stanford.edu/data.

\bibitem{mcbryde2009early}
McBryde E, Bergeri I, van Gemert C, Rotty J, Headley E, Simpson K, Lester R,
  Hellard M, and Fielding JE.
\newblock 2009 {Early transmission characteristics of influenza A (H1N1) v in
  Australia: Victorian state, 16 May--3 June 2009}.
\newblock {\em Euro Surveill}.
\newblock {\bfseries 14}, 19363.

\bibitem{roberts2011early}
Roberts MG and Nishiura H.
\newblock 2011 {Early estimation of the reproduction number in the presence of
  imported cases: pandemic influenza H1N1-2009 in New Zealand}.
\newblock {\em PLoS One}.
\newblock {\bfseries 6}, e17835.

\bibitem{trichereau2012estimation}
Trichereau J, Verret C, Mayet A, Manet G, Decam C, Meynard JB, Deparis X, and
  Migliani R.
\newblock 2012 {Estimation of the reproductive number for A (H1N1) pdm09
  influenza among the French armed forces, September 2009--March 2010}.
\newblock {\em J. Infect}.
\newblock {\bfseries 64}, 628--630.

\bibitem{nishiura2015theoretical}
Nishiura H and Chowell G.
\newblock 2015 Theoretical perspectives on the infectiousness of {Ebola} virus
  disease.
\newblock {\em Theor. Biol. Med. Model}.
\newblock {\bfseries 12}, 1.

\bibitem{szendroi2004polynomial}
Szendroi B and Cs{\'a}nyi G.
\newblock 2004 Polynomial epidemics and clustering in contact networks.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 271}, S364--S366.

\bibitem{chowell2015western}
Chowell G, Viboud C, Hyman JM, and Simonsen L.
\newblock 2015 {The Western Africa} {Ebola} virus disease epidemic exhibits
  both global exponential and local polynomial growth rates.
\newblock {\em PLoS Curr}.
\newblock 7.

\bibitem{chowell2016growing}
Chowell G and Viboud C.
\newblock 2016 Is it growing exponentially fast?--impact of assuming
  exponential growth for characterizing and forecasting epidemics with initial
  near-exponential growth dynamics.
\newblock {\em Infect. Dis. Model}.
\newblock {\bfseries 1}, 71--78.

\bibitem{chowell2016characterizing}
Chowell G, Viboud C, Simonsen L, and Moghadas SM.
\newblock 2016 Characterizing the reproduction number of epidemics with early
  subexponential growth dynamics.
\newblock {\em J. Royal Soc. Interface}.
\newblock {\bfseries 13}, 20160659.

\bibitem{kiskowski2016modeling}
Kiskowski M and Chowell G.
\newblock 2016 Modeling household and community transmission of {Ebola} virus
  disease: epidemic growth, spatial dynamics and insights for epidemic control.
\newblock {\em Virulence}.
\newblock {\bfseries 7}, 163--173.

\bibitem{viboud2016generalized}
Viboud C, Simonsen L, and Chowell G.
\newblock 2016 A generalized-growth model to characterize the early ascending
  phase of infectious disease outbreaks.
\newblock {\em Epidemics}.
\newblock 15, 27--37.

\bibitem{clarke1998contact}
Clarke J.
\newblock 1998 Contact tracing for chlamydia: data on effectiveness.
\newblock {\em Int. J. STD. AIDS}.
\newblock {\bfseries 9}, 187--191.

\bibitem{eames2003contact}
Eames KT and Keeling MJ.
\newblock 2003 Contact tracing and disease control.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 270}, 2565--2571.

\bibitem{donnelly2003epidemiological}
Donnelly CA, Ghani AC, Leung GM, Hedley AJ, Fraser C, Riley S, Abu-Raddad LJ,
  Ho~LM, Thach TQ, Chau P, and others .
\newblock 2003 Epidemiological determinants of spread of causal agent of severe
  acute respiratory syndrome in {Hong Kong}.
\newblock {\em Lancet}.
\newblock {\bfseries 361}, 1761--1766.

\bibitem{cauchemez2006estimating}
Cauchemez S, Bo{\"e}lle PY, Thomas G, and Valleron AJ.
\newblock 2006 Estimating in real time the efficacy of measures to control
  emerging communicable diseases.
\newblock {\em Am. J. Epidemiol}.
\newblock {\bfseries 164}, 591--597.

\bibitem{hens2012robust}
Hens N, Calatayud L, Kurkela S, Tamme T, and Wallinga J.
\newblock 2012 Robust reconstruction and analysis of outbreak data: influenza
  {A (H1N1)} v transmission in a school-based population.
\newblock {\em Am. J. Epidemiol}.
\newblock {\bfseries 176}, 196--203.

\bibitem{jewell2012enhancing}
Jewell CP and Roberts GO.
\newblock 2012 Enhancing {Bayesian} risk prediction for epidemics using contact
  tracing.
\newblock {\em Biostatistics}.
\newblock {\bfseries 13}, 567--579.

\bibitem{soetens2018real}
Soetens L, Klinkenberg D, Swaan C, Hahn{\'e} S, and Wallinga J.
\newblock 2018 Real-time estimation of epidemiologic parameters from contact
  tracing data during an emerging infectious disease outbreak.
\newblock {\em Epidemiology}.
\newblock {\bfseries 29}, 230--236.

\bibitem{anderson1980spread}
Anderson D and Watson R.
\newblock 1980 On the spread of a disease with gamma distributed latent and
  infectious periods.
\newblock {\em Biometrika}.
\newblock {\bfseries 67}, 191--198.

\bibitem{bailey1964some}
Bailey NT.
\newblock 1964 Some stochastic models for small epidemics in large populations.
\newblock {\em J. R. Stat. Soc. Ser. C. Appl. Stat}.
\newblock 13, 9--19.

\bibitem{bartlett1953stochastic}
Bartlett MS.
\newblock 1953 Stochastic processes or the statistics of change.
\newblock {\em J. R. Stat. Soc. Ser. C. Appl. Stat}.
\newblock {\bfseries 2}, 44--64.

\bibitem{gillespie1977exact}
Gillespie DT.
\newblock 1977 Exact stochastic simulation of coupled chemical reactions.
\newblock {\em J. Phys. Chem}.
\newblock {\bfseries 81}, 2340--2361.

\bibitem{newman2003structure}
Newman ME.
\newblock 2003 The structure and function of complex networks.
\newblock {\em SIAM Rev}.
\newblock {\bfseries 45}, 167--256.

\bibitem{daley2007introduction}
Daley DJ and Vere-Jones D.
\newblock 2007 {\em {An introduction to the theory of point processes: volume
  II: general theory and structure}}.
\newblock Springer Science \& Business Media.

\bibitem{lagakos1988nonparametric}
Lagakos SW, Barraj LM, and Gruttola Vd.
\newblock 1988 {Nonparametric analysis of truncated survival data, with
  application to AIDS}.
\newblock {\em Biometrika}.
\newblock {\bfseries 75}, 515--523.

\bibitem{kalbfleisch1991regression}
Kalbfleisch J and Lawless J.
\newblock 1991 {Regression models for right truncated data with applications to
  AIDS incubation times and reporting lags}.
\newblock {\em Statistica Sinica}.
\newblock pages 19--32.

\bibitem{kalbfleisch1989inference}
Kalbfleisch J and Lawless JF.
\newblock 1989 {Inference based on retrospective ascertainment: an analysis of
  the data on transfusion-related AIDS}.
\newblock {\em J. Am. Stat. Assoc}.
\newblock {\bfseries 84}, 360--372.

\bibitem{king2015avoidable}
King AA, de~Celles MD, Magpantay FM, and Rohani P.
\newblock 2015 Avoidable errors in the modelling of outbreaks of emerging
  pathogens, with special reference to {Ebola}.
\newblock {\em Proc. R. Soc. B}.
\newblock {\bfseries 282}, 20150347.

\bibitem{leskovec2007graph}
Leskovec J, Kleinberg J, and Faloutsos C.
\newblock 2007 Graph evolution: {Densification} and shrinking diameters.
\newblock {\em ACM T. Knowl. Discov. D.}
\newblock {\bfseries 1}, 2.

\end{thebibliography}

\end{document}
